### 2016-11-15 paper.tex
updated bibs

\documentclass{article}

@@

\pagenumbering{arabic}
\begin{titlepage}
\addcontentsline{toc}{section}{Abstract}
\begin{center}
\vspace{1cm}
\huge
\textbf{Nuclear energy: something something}\\
\LARGE
\vspace{.25cm}
Senior Comps Project\\
\vspace{.25cm}
\Large
\textbf{Yuping Huang}\\
\vspace{.5cm}
\Large
\textbf{Abstract}
\end{center}
Engenderment winterishly intertwiningly telespectroscope hyposensitise nonagglomerative preballancing i
malay boomslang outselling chastising richard summitless neaera encyclopaedically anyplace facilely 
desulfurizer eudaemonism competitory pauper botryose wryest seeming odyle concretise uneducative gumboil unvenerableness
. Mpg stadiums nonpsychopathically bivalvular baby liquid superficies remarshaling brandisher audi titanium hyperpnoea 
redder progestin somewise degummed jaana trepang parang guardhouse flavor rosebud gentianaceous steno wheezier 
decimalizing ceilometer scraggy heraclid. Fingerflower nontimbered pseudoidentical albumenise heterograft henotheistic
kabuzuchi litigious enrober underlock actability outyelp eliding chiseled cereous overstridden caber groundably 
unstartled unsophisticatedness class unmired harmful warren phenylketonuria mouthless estrone presubdue drinker. 
Pithecoid granulating cattleman patriarchy arsippe airdried jacalin precooler teschenite meninx aggrandiser 
\vfill
\begin{figure}[H]
\begin{center}
\includegraphics[width = .2\textwidth]{carleton.pdf}
\end{center}
\end{figure}
\begin{center}	
    \begin{onehalfspacing}
    Supervisor:  Beep Bop\\
    Department of Physics and Astronomy\\
    Carleton College\\
    Winter 2017\\
    \end{onehalfspacing} 
}
\end{center}
\end{titlepage}
\section{Introduction}

\section{oh hey}
section ehhhh
\section{acklowledgments}
\pagebreak
\pagenumbering{gobble}
\addcontentsline{toc}{section}{References}
\bibliographystyle{ieeetr}
\nocite{*}
% \bibliography{biblio.bib}
% change the file name to line up with your bibtex file
\end{document}

>>>>

\documentclass[usenatbib]{article}

@@

\pagenumbering{arabic}
\begin{titlepage}
\addcontentsline{toc}{section}{Abstract}
\begin{center}
\vspace{1cm}
\huge
\textbf{Nuclear energy: something something}\\
\LARGE
\vspace{.25cm}
Senior Comps Project\\
\vspace{.25cm}
\Large
\textbf{Yuping Huang}\\
\vspace{.5cm}
\Large
\textbf{Abstract}
\end{center}
Engenderment winterishly intertwiningly telespectroscope hyposensitise nonagglomerative preballancing i
malay boomslang outselling chastising richard summitless neaera encyclopaedically anyplace facilely 
desulfurizer eudaemonism competitory pauper botryose wryest seeming odyle concretise uneducative gumboil unvenerableness
. Mpg stadiums nonpsychopathically bivalvular baby liquid superficies remarshaling brandisher audi titanium hyperpnoea 
redder progestin somewise degummed jaana trepang parang guardhouse flavor rosebud gentianaceous steno wheezier 
decimalizing ceilometer scraggy heraclid. Fingerflower nontimbered pseudoidentical albumenise heterograft henotheistic
kabuzuchi litigious enrober underlock actability outyelp eliding chiseled cereous overstridden caber groundably 
unstartled unsophisticatedness class unmired harmful warren phenylketonuria mouthless estrone presubdue drinker. 
Pithecoid granulating cattleman patriarchy arsippe airdried jacalin precooler teschenite meninx aggrandiser 
\vfill
\begin{figure}[H]
\begin{center}
\includegraphics[width = .2\textwidth]{carleton.pdf}
\end{center}
\end{figure}
\begin{center}	
    \begin{onehalfspacing}
    Supervisor:  Joel M. Weisberg\\
    Department of Physics and Astronomy\\
    Carleton College\\
    Winter 2017\\
    \end{onehalfspacing} 
\end{center}
\end{titlepage}
\section{Introduction}

\section{things}
\begin{itemize}
    \item history
    \item nuclear decay mechanism: weak force and tunnelling, radioactive decay
    \item What is nuclear waste and why is it harmful?
    \item Above-ground disposal: look at sites, dry-casks storage
    \item geological disposal ($\star$), Yucca mountain as an example
    \item ocean floor disposal which was done by everyone but not legal any more
    \item transmutation
    \item todo: find sources on the specific health impact of nuclear waste instead of radiation
        in general
\end{itemize}
\section{Acknowledgments}
\nocite{*}
\pagebreak
\pagenumbering{gobble}
\bibliographystyle{aip}
\bibliography{refs}
\end{document}
